---
title: "QLF survey analysis"
output:
  html_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```
```{r}
library(tidyverse)
library(readr)
library(janitor)
```


```{r}
implement_principles <- qlf_principles_affiliates_clean %>% 
  select(neighborhood, contains("implement_")) %>% 
```

#Principles in practice

Across the 10 affiliates, fostering partnerships is the principle most commonly put into practice in neighborhood revitalization efforts. While on average affiliates indicated implementing most principles to a moderate (4) or a large (5) extent, there is opportunity for improvement particularly in focusing on systems which had the lowest average.

```{r}
implement_principles <- qlf_principles_affiliates_for_r %>% 
  select(neighborhood, contains("implement_")) %>% 
  mutate(impl_part_num = case_when(
    implement_partnerships == "Not at all" ~ "1",
    implement_partnerships == "To a small extent" ~ "2",
    implement_partnerships == "To some extent" ~ "3",
    implement_partnerships == "To a moderate extent" ~ "4",
implement_partnerships == "To a large extent" ~ "5")) %>% 
  mutate(impl_part_num = as.numeric(impl_part_num))
  
implement_principles <- implement_principles %>% 
  mutate(impl_build_num = case_when(
    implement_build_power == "Not at all" ~ "1",
    implement_build_power == "To a small extent" ~ "2",
    implement_build_power == "To some extent" ~ "3",
    implement_build_power == "To a moderate extent" ~ "4",
    implement_build_power == "To a large extent" ~ "5")) %>% 
  mutate(impl_build_num = as.numeric(impl_build_num))

implement_principles <- implement_principles %>% 
  mutate(impl_acct_num = case_when(
    implement_accountability == "Not at all" ~ "1",
    implement_accountability == "To a small extent" ~ "2",
    implement_accountability == "To some extent" ~ "3",
    implement_accountability == "To a moderate extent" ~ "4",
    implement_accountability == "To a large extent" ~ "5")) %>% 
  mutate(impl_acct_num = as.numeric(impl_acct_num))

implement_principles <- implement_principles %>% 
  mutate(impl_learn_num = case_when(
    implement_learn == "Not at all" ~ "1",
    implement_learn == "To a small extent" ~ "2",
    implement_learn == "To some extent" ~ "3",
    implement_learn == "To a moderate extent" ~ "4",
    implement_learn == "To a large extent" ~ "5")) %>% 
  mutate(impl_learn_num = as.numeric(impl_learn_num))

implement_principles <- implement_principles %>% 
  mutate(impl_systems_num = case_when(
    implement_systems == "Not at all" ~ "1",
    implement_systems == "To a small extent" ~ "2",
    implement_systems == "To some extent" ~ "3",
    implement_systems == "To a moderate extent" ~ "4",
    implement_systems == "To a large extent" ~ "5")) %>% 
  mutate(impl_systems_num = as.numeric(impl_systems_num))

implement_principles_pivot <- implement_principles %>%
  select(neighborhood, contains ("impl_")) %>% 
  pivot_longer(cols = -neighborhood,
                             names_to = "principle",
                             values_to = "value")

implement_principles_avg <- implement_principles_pivot %>% 
 group_by(principle) %>% 
  summarize(mean = mean(value)) %>% 
  arrange(desc(mean))
  
  ggplot(data = implement_principles_avg, 
       mapping = aes(x = principle, 
                     y = mean,
                     fill = principle
                     )) +
  geom_col(show.legend = FALSE)+
  geom_text(aes(label = mean),
            vjust = 1.5,
            color = "black")
```


